\documentclass[10pt,a4paper,roman]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}
\firstname{\textsc{Adedeji}}
\familyname{\textsc{Adepetun}}
\title{}
\address{27, Barnaby Rudge}{CM1 4YG}{Chelmsford}
\phone[mobile]{+447903619212}
\email{dejiadepetun@gmail.com}              
%\social[github]{deji-adepetun}

\moderncvhead{3}
\moderncvbody{1}

\begin{document}
\makecvtitle

\section{\textsc{Profile}}
\cvitem{}{
A recent graduate with a Distinction in Advanced Computer Science from the University of Manchester and a 2.1 in Mechanical Engineering from the University of Sheffield.
Possessing relevant academic and technical experience gained during my academic degrees.}
\cvitem{}{
Able to balance competing priorities having worked part-time during my undergraduate degree.
Looking to secure a graduate role which will provide industrial exposure and the opportunity for career progressions.}

\section{\textsc{Education}}
\cventry{2016 -- 2018}{MSc. Advanced Computer Science}{Distinction}{University of Manchester}{}{}
\cvitem{Thesis}{Piquet: An AI program that plays a game of Piquet using the Information Set Monte Carlo Tree Search algorithm and heuristic domain knowledge.}
\cventry{2013 -- 2016}{BEng Mechanical Engineering}{2:1}{University of Sheffield}{}{}
\cvitem{Thesis}{Full Scale 40MW Coal Burner design: Design of a full scale coal burner limiting coal combustion NO\textsubscript{x} emissions using ANSYS Fluent analysis.}
\cvitem{Awards}{Undergraduate Award for Academic Achievement}

\section{\textsc{Work Experience}}
\cventry{October 2015 -- June 2016}{Teaching Assistant}{University of Sheffield}{Sheffield}{United Kingdom}
{Mathematics for Engineering Modelling, Computational and Numerical Methods.
\begin{itemize}
	\item Assisted in the grading of module lab work.
	\item Explaining foundational concepts to students.
\end{itemize}}

\cventry{July -- September 2015}{Mechanical Engineering Intern}{Bristow Group}{Lagos}{Nigeria}
{Worked with the Bristow Aviation Technical Services (BATS) branch of the company.
\begin{itemize}
	\item Performed maintenance checks on Sikorsky helicopters under the supervision of a senior staff member.
	\item Organised the maintenance timetable for the helicopter hangar.
\end{itemize}}

\section{\textsc{Interests}}
\cventry{October 2014 -- July 2016}{Mechanical Engineering Academic Representative}{Mechanical Engineering Society}{University of Sheffield}{}{
\begin{itemize}
	\item Represent student interests to the academic department.
	\item Acted as a liaison between the student body and the academic staff.
\end{itemize}}
\cventry{September 2014 -- July 2015}{Working Committee Member}{International Students Committee}{University of Sheffield}{}{
\begin{itemize}
	\item Volunteered for the World Week parade, Language festival, International Cultural Evening.
	\item Helped with advertisements of committee projects, increasing the project outreach.
\end{itemize}}

\section{\textsc{Volunteering}}
\cventry{September 2014 -- May 2016}{Peer Assisted Study Session Leader}{University of Sheffield Career Services}{University of Sheffield}{}{
\begin{itemize}
	\item Member of the pioneering PASS team and created a strong and viable foundation for the PASS initiative.
	\item Provided mentorship for several undergraduate students in the Mechanical Engineering department.
\end{itemize}}

\clearpage
\section{\textsc{Projects}}
\subsection{Academic}
\cventry{}{"What's that pet?" application}{}{}{}{
\begin{itemize}
	\item Predicts the type of pet from a picture using a convolutional neural network.
	\item Languages used: Python, numpy, TensorFlow, Javascript, JQuery, HTML, CSS.
\end{itemize}}
\cventry{}{Journal management web application}{}{}{}{
\begin{itemize}
	\item Web application that manages a library of academic journals.
	\item Used a agile and test-driven development approach.
	\item Languages and frameworks used: Python, Flask, HTML, CSS, Javascript, d3.js.
\end{itemize}}
\subsection{Personal}
\cventry{}{A\textsuperscript{*} Pathfinding Visualisation Application}{}{}{}{
\begin{itemize}
	\item A Java Swing application for the visualisation of the A\textsuperscript{*} pathfinding algorithm.
	\item Languages used: Java, Swing, A\textsuperscript{*} pathfinding algorithm.
\end{itemize}}

\section{\textsc{Skills}}
\cventry{}{Self-taught}{Java, Python, Javascript, SQL, HTML, CSS}{}{}{}
\cventry{}{Academically-taught}{MATLAB, SPARQL, XML, Flask, JQuery}{}{}{}
\cventry{}{Intermediate Knowledge}{C\#, PHP, AngularJS, React, Bootstrap}{}{}{}


\clearpage
\end{document}

}